### 2021-03-27 papers.tex
all the ontime papers and some reviews

	{AI is a Really, Really, Really Bad Idea}
	{Molly de Blanc}
	{Keywords: artificial intelligence, ethics, machine learning}

@@

>>>>

%\addpaper
%	{AI is a Really, Really, Really Bad Idea}
%	{Molly de Blanc}
%	{Keywords: artificial intelligence, ethics, machine learning}
%	{SIGBOVIK_2021_paper_10}
%	{0cm}
%	{}

@@

	{A Note on ``The Consent Hierarchy''}
	{Anonymous Nobody}
	{Keywords: freely given, reversible, informed, enthusiastic, specific}
	{SIGBOVIK_2021_paper_25}
	{Lowestcase and uppestcase letters: Advances in derp learning}
	{Tom Murphy VII}
	{case analysis, derp learning, 3d manifold, chess, exponentiation, fonts}
	{SIGBOVIK_2021_paper_26}

\addpaper
	{Soliterrible}
	{Sam Stern}
	{Keywords: solitaire, klondike, cards}
	{SIGBOVIK_2021_paper_27}
	{0cm}
	{}

\addpaper
	{Another Thorough Investigation of the Degree to which the COVID-19 Pandemic has Enabled Subpar-Quality Papers to Make it into SIGBOVIK, by Reducing the Supply of Authors Willing to Invest the Necessary Effort to Produce High-Quality Papers}
	{Shalin Shah}
	{Keywords: SIGBOVIK, COVID-19, Lazy, Low-Effort, Subpar-Quality}
	{SIGBOVIK_2021_paper_28}
	{0cm}
	{}
\addpaper
	{Spacecraft Attitude Determination and Control}
	{Freddie Rawlins}
	{Keywords: attitude, determination, happy satellites}
	{SIGBOVIK_2021_paper_29}
	{0cm}
	{}
\addpaper
	{A Complete Survey of 0-Dimensional Computer Graphics}
	{Hesper Yin, Oscar Dadfar, Max Slater, Anne He, Alice Lai, Emma Liu and Ryan Po}
	{Keywords: Computer Graphics, Geometry, Rendering, Animation}
	{SIGBOVIK_2021_paper_30}
	{0cm}
	{}
\addpaper
	{Macro-driven metalanguage for writing Pyramid Scheme programs}
	{Marcin Konowalczyk}
	{Keywords: syntax tree, pyramids, compilation, horizontal gene transfer, sorting, code golf}
	{SIGBOVIK_2021_paper_31}
	{0cm}
	{}
\addpaper
	{On the fundamental impossibility of refining the Theory of Everything by empirical observations: a computational theoretic perspective}
	{Zikuan Wang}
	{Keywords: Theory of Everything, Cellular Automaton, Emulation, the Universe}
	{SIGBOVIK_2021_paper_32}
	{0cm}
	{}
\addpaper
	{On the dire importance of MRU caches for human survival (against Skynet)}
	{Darío de la Fuente García, Félix Áxel Gimeno Gil, Juan Carlos Morales Vega and Borja Rodríguez Gálvez}
	{Keywords: Skynet, MS paint, cache, MRU, dMRU, sMRU, NEP}
	{SIGBOVIK_2021_paper_33}
	{0cm}
	{}
\addpaper
	{Dependent Stringly-Typed Programming}
	{G. Allais}
	{Keywords: dependent stringly typed programming, best practices, agda}
	{SIGBOVIK_2021_paper_34}
	{0cm}
	{}
\addpaper
	{Yet Another Lottery Ticket Hypothesis}
	{Aman Madaan and Gary Yao}
	{Keywords: lottery, random, language models}
	{SIGBOVIK_2021_paper_35}
	{0cm}
	{}
\addpaper
	{Yet Another Lottery Ticket Hypothesis}
	{Aman Madaan and Gary Yao}
	{Keywords: lottery, random, language models}
	{SIGBOVIK_2021_paper_36}
	{0cm}
	{}
\addpaper
	{Yet Another Lottery Ticket Hypothesis}
	{Aman Madaan and Gary Yao}
	{Keywords: lottery, random, language models}
	{SIGBOVIK_2021_paper_37}
	{0cm}
	{}
\addpaper
	{Yet Another Lottery Ticket Hypothesis}
	{Aman Madaan and Gary Yao}
	{Keywords: lottery, random, language models}
	{SIGBOVIK_2021_paper_38}
	{0cm}
	{}
\addpaper
	{Yet Another Lottery Ticket Hypothesis}
	{Aman Madaan and Gary Yao}
	{Keywords: lottery, random, language models}
	{SIGBOVIK_2021_paper_39}
	{0cm}
	{}
\addpaper
	{Yet Another Lottery Ticket Hypothesis}
	{Aman Madaan and Gary Yao}
	{Keywords: lottery, random, language models}
	{SIGBOVIK_2021_paper_40}
	{0cm}
	{}
\addpaper
	{Yet Another Lottery Ticket Hypothesis}
	{Aman Madaan and Gary Yao}
	{Keywords: lottery, random, language models}
	{SIGBOVIK_2021_paper_41}
	{0cm}
	{}
\addpaper
	{Yet Another Lottery Ticket Hypothesis}
	{Aman Madaan and Gary Yao}
	{Keywords: lottery, random, language models}
	{SIGBOVIK_2021_paper_42}
	{0cm}
	{}
\addpaper
	{Yet Another Lottery Ticket Hypothesis}
	{Aman Madaan and Gary Yao}
	{Keywords: lottery, random, language models}
	{SIGBOVIK_2021_paper_43}
	{0cm}
	{}
\addpaper
	{Yet Another Lottery Ticket Hypothesis}
	{Aman Madaan and Gary Yao}
	{Keywords: lottery, random, language models}
	{SIGBOVIK_2021_paper_44}
	{0cm}
	{}

\addreview
	{SIGBOVIK_2021_review_1}
	{0cm}

### 2021-03-27 reviews/SIGBOVIK_2021_review_2.tex
all the ontime papers and some reviews

%%%% Edit the following three lines.
%% To ensure the integrity of the triple-blind review
%% process, the contents of the \author field should not
%% reveal your identity.
\author{Maya Harris, undergraduate student.}
\rating{6/10, 9/10 with rice.}
\confidence{100\%. Ok, fine. 95\%, since I know certainty freaks you out.}

@@

\subsection{Introduction}
Let me go! NO! You can't force me to read this! I already read enough on reddit. I don't care that you can't find any reviewers because of COVID-19. That's your problem (Shah, 2020). Let me GO! I said, let ME GO!

**muffled voices, struggling**

\subsection{Methods}
No one cares what your journal's impact factor is. What even is that? What do you expect me to say here? I barely listen in lectures and just wing all my homework. I don't even know what the difference between Windows and Linux is. I signed up for university to get a real job at FAANG or even Tesla so I can at least get my foot in the door in the valley, not help propagate your academic pyramid scheme. NO! I barely know how to read! Who cares about science or fun???? There's money to be made in industry. I want money.

**a door shuts**

**Rick Astley -- Never Gonna Give You Up starts to play on repeat in the closed room and the sound of water dripping echoes**

\textit{forty hours later}

\subsection{Results}
Ok, ok, ok. Just stop the music. Just, please, stop the music. I read the paper. I filled out all the sections from the template you gave me from autoreject.org, ok? I signed the thing that says I did this of my own free will and have no conflicts of interest.

\subsection{Discussion}
But you know, it actually really liked the article, so if you decide to accept -- what? You publish even papers even if reviewers recommend reject? How does that make any sense?

\subsection{Conclusion}
Ok whatever. Can I go now?

\subsection{References}

Shah, S. (2020). A Thorough Investigation of the Degree to which the COVID-19 Pandemic has Enabled Subpar-Quality Papers to Make it into the Proceedings of SIGBOVIK, by Reducing the Supply of Authors Willing to Invest the Necessary Effort to Produce High-Quality Papers. \textit{SIGBOVIK 2020}. URL: http://sigbovik.org/2020/proceedings.pdf

>>>>

%%%% Edit the following three lines.
%% To ensure the integrity of the triple-blind review
%% process, the contents of the \author field should not
%% reveal your identity.
\author{Hans-Peter Rüdisühli, Jasskönig vo de mittlere und vierte Schattegibeleggtäli}
\rating{Ahxeyt Zwöi, gmacht Driezäh, Difäränz Öuf!}
\confidence{Ha dänkt är loufi no is Näuu...}

@@

%%% Replace the following text with your review.
D'Chnäbäschterete vo dem Chlampf laht sich nid ring zämefasse, düecht mi aber es gröizigs Gspüder. Obwou hie wichtigi Erkenntnis us Schöppelimunggi, Houderebäsler, \& Totemügerli (1967) nid prantlet wärde, gstabets guet gfroorig u gäng no mappelig. Bsungers d'Hagletsche vo drobertrolige Spänkmügge wird vo buschtränggeligem Fodelebank sii u gürblet s'Bstotzige. Söu gäute!

### 2021-03-27 reviews/SIGBOVIK_2021_review_3.tex
all the ontime papers and some reviews

%%%% Edit the following three lines.
%% To ensure the integrity of the triple-blind review
%% process, the contents of the \author field should not
%% reveal your identity.
\author{Hans-Peter Rüdisühli, Jasskönig vo de mittlere und vierte Schattegibeleggtäli}
\rating{Ahxeyt Zwöi, gmacht Driezäh, Difäränz Öuf!}
\confidence{Ha dänkt är loufi no is Näuu...}

@@

%%% Replace the following text with your review.
D'Chnäbäschterete vo dem Chlampf laht sich nid ring zämefasse, düecht mi aber es gröizigs Gspüder. Obwou hie wichtigi Erkenntnis us Schöppelimunggi, Houderebäsler, \& Totemügerli (1967) nid prantlet wärde, gstabets guet gfroorig u gäng no mappelig. Bsungers d'Hagletsche vo drobertrolige Spänkmügge wird vo buschtränggeligem Fodelebank sii u gürblet s'Bstotzige. Söu gäute!

>>>>

%%%% Edit the following three lines.
%% To ensure the integrity of the triple-blind review
%% process, the contents of the \author field should not
%% reveal your identity.
\author{Reviewer Number Two-and-a-half}
\rating{Excellent paper!}
\confidence{Absolutely bloody confident, as always!}

@@

%%% Replace the following text with your review.
\textbf{Excellent paper} -- truly marvellous! With a whiteness of 144, and an opacity of well over ninety percent, this paper promises excellent colour reproduction, which will be highly desirable for printing the inevitable graphs. Furthermore, this paper's grammage -- 80$g/m^2$ -- is fit for purpose, and keeps the price in check. Our proceedings need more paper of this calliper!

### 2021-03-27 reviews/SIGBOVIK_2021_review_4.tex
all the ontime papers and some reviews

%%%% Edit the following three lines.
%% To ensure the integrity of the triple-blind review
%% process, the contents of the \author field should not
%% reveal your identity.
\author{\textless ix@tchow.com\textgreater}
\rating{\textless sigbovik@gmail.com\textgreater}
\confidence{Re: Draft 2020 proceedings!}

%%%% The Proceedings Chair will fill in the following
%%%% two fields.
\papernum{Review of Paper 31}
\papertitle{The SIGBOVIK 2020 field guide to plants}

@@

%%% Replace the following text with your review.
I think the review currently for the guide to plants should probably be attributed to the originator of the couplet (Edward Lear) rather than to "Prof. Jim McCann" -- I'm not sure there's much joke added (since it ended up on a paper referencing me) and I'm not really comfortable with something I didn't write being attributed to me.

-{}-Jim

>>>>

%%%% Edit the following three lines.
%% To ensure the integrity of the triple-blind review
%% process, the contents of the \author field should not
%% reveal your identity.
\author{Reviewer from the future}
\rating{10}
\confidence{10}

%%%% The Proceedings Chair will fill in the following
%%%% two fields.
\papernum{NN}
\papertitle{UNKNOWN PAPER TITLE}

@@

I have come from the future to review this paper.
In the year 2035 time travel is invented. This paper is/was/will be the key to making it possible! At the time, I understand it was not terrifically well-received, due to its seeming lack of rigor, which admittedly did impede our understanding of its methods, likely causing a few years of delay. Thus, I have been assigned to make sure it gets accepted.

Unfortunately, this paper also indirectly resulted in an imminent grey goo scenario. Well, you win some, you lose some.
